---
title: "MarkdownReport"
author: "Paula Garbin"
date: "2024-01-09"
output: html_document
---

# My first markdown document!            
 In Rmarkdown # is a title 

Here you can add some text if you want! 
# RMarkDown file!
In this case you obtain a result:
```{r, eval=T}             state to the software what language we are using and if we want to run the code or not 
 2+3                       language is r, if code should lead to the result or not (eval=T or F)
```

In this case you do not:
```{r, eval=F}            
 2+3                     
```

Using proper packages; the imageRy package has been built at Alma Mater for learning remote sensing:
```{r, eval=T}            
 library(imageRy)                   
```

Lets import some data by listing them in imageRy:
```{r, eval=T}
 im.list()                   
```

Importing the Mato Grosso area image and excluding warnings: 
```{r, eval=T, warning=F}
 mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")                  
```

In order to get information on the image, just type the name of the object: 
```{r, eval=T}
mato1992                  
```

Making a new plot of the Mato Grosso area with the NIR on top of the green component of 
the RGB space: 
```{r, eval=T}
im.plotRGB(mato1992, r=2, g=1, b=3)                 
```

Plotting several images altogether: 
```{r, eval=T}
par(mfrow=c(2,2))
im.plotRGB(mato1992, r=1, g=2, b=3) 
im.plotRGB(mato1992, r=2, g=1, b=3)
im.plotRGB(mato1992, r=3, g=2, b=1) 
im.plotRGB(mato1992, r=2, g=1, b=1) 
```

Calculating spectral indices:
```{r, eval=T}
library(viridis)
dvi <- mato1992[[1]]-mato1992[[2]]
viridisc <- colorRampPalette(viridis(7))(255)
plot(dvi, col=viridisc)
```


